Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-15 analysis/paper/paper.Rmd
Replace TPP reference with proper reference

Recently, open science has been highlighted with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@TPP2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].

>>>>

Recently, open science has been highlighted with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
